### 2024-12-10 draft.tex
Added Draft Outline of Thesis and Introduction

\section*{Draft ideas}
\subsection{Abstract}
\begin{itemize}
    \item What is the CLT? Why is formal verification important?
    \item What limitations or gaps does this work address?
    \item Briefly summarize the methods, results, and significance.
\end{itemize}

\subsection{Introduction}
\cite{tian2022assumption}
\cite{qasim2016formalization}
\begin{itemize}
    \item What is CLT
    \item Define the CLT in its simplest form (e.g., i.i.d. random variables)
    \item Highlight its importance in statistics, machine learning, and other fields as a foundation for normal approximation.
\end{itemize}

\subsubsection{Motivation}
Why formalize the CLT in HOL4? 
The challenges with probabilistic reasoning, the need for rigor, and the importance of verifying a key theorem like the CLT.
\begin{itemize}
    \item Enriching the HOL4 Theory Library
    \item Supporting Future Applications
    \item Providing Analytical Tools
\end{itemize}

\subsubsection{Contributions}
\begin{itemize}
    \item This thesis proves the Lyapunov version of the Central Limit Theorem, a fundamental result in probability theory. The CLT of Lyapunov extends the classical CLT by relaxing the identical distribution assumption to the case of independent but not necessarily identically distributed random variables.
    \item The proof makes use of Taylor expansions, moment-based bounds, and asymptotic error analysis to rigorously establish convergence to the normal distribution.
    \item The main insights involve the Lyapunov condition, which guarantees that the third absolute moments become small compared to the variance, and a new use of Big-O notation for the effective control of error terms.
\end{itemize}

\subsubsection{Results}
This form of CLT is more general than the i.i.d case but not the most general (not the Lindeberg-Feller version).

\begin{itemize}
    \item \textbf{Lyapunov CLT}: For independent random variables \(X_1, X_2, \ldots, X_n \) with finite means, variances, and third moments, if the Lyapunov condition is satisfied:
$$
\frac{\Gamma_n}{s_n^3} \to 0 \quad \text{as } n \to \infty,
$$
then the normalized sum \( \frac{S_n - \mu}{s_n} \) converges in distribution to the standard normal distribution \( N(0, 1) \).
    \item \textbf{Proof}: It establishes that
    \begin{itemize}
        \item Error bounds of the test function \(f\) by Taylor expansion and moment inequalities.
        \item Asymptotic vanishing of higher-order terms under the Lyapunov condition.  \item A rigorous comparison between the distribution of \( \frac{S_n}{s_n} \) and \( N(0, 1)\), bounded by \( O\left(\frac{\Gamma_n}{s_n^3}\right) \).
    \end{itemize}

These results illustrate the robustness of the Lyapunov CLT against heterogeneous distributions and, in fact, form a bridge between classical formulations and modern applications.

Also, highlight key formal results of other lemmas and theorems to support (e.g., bounding errors using Big-O, weak convergence).
\end{itemize}

\subsection{Background and Related Works}
\subsubsection{Historical Background}
Introduce the histrory of CLT and mention different versions of CLT \cite{fischer2011history}
\begin{itemize}
    \item Classical versions: De Moivre-Laplace (i.i.d.), Lindeberg-Feller, Lyapunov’s theorem.
    \item Explain why Lyapunov’s version is chosen (finite moments, no characteristic functions).
\end{itemize}

\begin{itemize}
    \item \textbf{Classical Central Limit Theorem} \cite{ross2019first}
    \begin{itemize}
        \item \textbf{Proven by:} De Moivre, Laplace
        \item \textbf{Statement:} If \( X_1, X_2, \ldots, X_n \) are independent and identically distributed (i.i.d.) random variables with finite mean \( \mu \) and variance \( \sigma^2 \), then:
  \[
  Z_n = \frac{\sum_{i=1}^n X_i - n\mu}{\sigma\sqrt{n} } \xrightarrow{d} N(0, 1).
  \]
  \item \textbf{Significance:} Foundation of probability theory and statistics, used in inferential statistics, e.g., hypothesis testing and confidence intervals.
    \end{itemize}

    \item \textbf{Lyapunov’s Central Limit Theorem} \cite{chung2000course}
    \item \textbf{Lindeberg’s Central Limit Theorem}
    \item \textbf{The Generalized Central Limit Theorem} 
    \begin{itemize}
        \item https://en.wikipedia.org/wiki/Central_limit_theorem
    \end{itemize}

\end{itemize}

\subsubsection{Related Work}
The CLT is a fundamental result in probability theory, and its formalization in theorem provers has been a highly active area of interest in the formal methods community. Several different ways of proving the CLT have been tried, and tools like Isabelle/HOL and HOL4 provide different approaches reflecting their different frameworks and mathematical libraries.

\textbf{Isabelle/HOL's Formalization of the CLT}
In Isabelle/HOL, the CLT has been formalized in a powerful and especially elegant way using the \textbf{characteristic function approach}, which relies on the fact that characteristic functions uniquely determine probability distributions and their pointwise convergence implies convergence in distribution.
\cite{serafin2015formally}

\begin{itemize}
    \item \textbf{Methodology}
    \item \textbf{Characteristic Function Approach}
    \begin{itemize}
        \item It provides a direct and compact route to proving the CLT, leveraging the algebraic simplicity of characteristic functions.
        \item ...
    \end{itemize}
\end{itemize}

\subsubsection{Overview of Informal Proof}
\begin{itemize}
    \item Highlight the direct and real-valued approach of Lyapunov's proof.
    \item Discuss how it avoids characteristic functions and instead uses bounding error terms (Taylor expansion, Big-O).
\end{itemize}

\subsection{Preliminaries}
\subsubsection{HOL4}
\cite{tian2022assumption}
\subsubsection{Measure Theory}
\cite{qasim2016formalization}
\subsubsection{Lebesgue Integration Theory}
\cite{qasim2016formalization}
\subsubsection{Probability Theory}
\cite{qasim2016formalization}

\newpage
\subsection{The proof of Central Limit Theorem}
\subsubsection{Informal Proof}
Informal proof of Lyapounov's theorem for a single sequence by the method of Lindeberg \cite{chung2000course}.
\begin{itemize}
    \item \textbf{Notation and Statement}
    \begin{enumerate}
    \item \( \{X_j\}_{j=1}^n \) be a sequence of independent random variables with:
    \begin{itemize}
        \item[] \( \mathbb{E}[X_j] = 0 \), 
        \item[] \( \text{Var}(X_j) = \sigma_j^2 \) (finite variances, \( \sigma_j^2 < \infty \)),
        \item[] \( \mathbb{E}[|X_j|^3] = \gamma_j \) (finite third moments, \( \gamma_j < \infty \)).
    \end{itemize}

@@

\subsubsection{Formal Proof in HOL4}
Key lemmas and theorems:
\begin{itemize}
    \item Weak convergence
    \item Taylor expansion of expectations
    \item Big-O bounds for error terms
\end{itemize}

\subsection{Limitations and Future Directions}
\subsubsection{Limitations}
\begin{itemize}
    \item Mention limitations in HOL4’s current libraries: Incomplete ComplexTheory, which prevents characteristic function-based proofs, Lack of direct support for third moments of normal random variables, making certain bounds harder to verify formally.
    \item This work is for proof of Lyapunov’s version, which is more general than the i.i.d. case but not the most general form (e.g., Lindeberg-Feller).
\end{itemize}

\subsubsection{Future Directions}
\begin{itemize}
    \item Explore the possibility of extending HOL4 to include: Characteristic functions and ComplexTheory, and A general Lindeberg-Feller version of the CLT.    
\end{itemize}

\subsection{Conclusions}
The CLT is a fundamental result in probability theory, ranging from mathematics and statistics to finance and data science. This work described the formal proof of the CLT using Lyapunov's criterion in the HOL4 theorem prover. The proof showed that the normalized sum of independent (but not necessarily identically distributed) random variables converges in distribution to the standard normal distribution by exploiting a moment-based approach along with Lyapunov's condition.

\textbf{Conclusions}
\begin{itemize}
    \item \textbf{Formalization of Lyapunov's CLT}
    \begin{itemize}
        \item The proof formalized Lyapunov's version of the CLT by providing rigorous bounds on error terms and establishing convergence under the Lyapunov condition. The use of Big-O notation and asymptotic error analysis was instrumental in managing higher-order terms.
    \end{itemize}

    \item \textbf{Theoretical Insights}
    \begin{itemize}
        \item In addition, a constructive, moment-based methodology used in its proof gave a natural perspective on finite variances and higher-order moments, each playing an important part in ensuring convergence according to CLT.
    \end{itemize}

    \item \textbf{Comparison with Previous Works}
    \begin{itemize}
        \item The approach represents a complementary alternative to existing formalizations, such as \textbf{Isabelle/HOL's characteristic function-based proof}, in that it represents a constructive proof based on explicit bounds and moment inequalities. It is also an addition to the variety of formalizations and expands the reach of theorem provers regarding probabilistic results.
    \end{itemize}

\end{itemize}
Formalization of CLT in HOL4 showcases the power of theorem provers in the formal verification of fundamental results in probability theory. It fills the gap between theoretical results and their verification by computation, showing the potential of formal methods in academic and applied domains.

In closing, this thesis provides not only a sound formalization of Lyapunov's CLT but also the whole range of insights into what happens when formal methods are integrated with probability theory. It lays the ground for further investigations into probabilistic results within theorem provers, opening perspectives to theoretical advances as well as practical applications.

>>>>

\section*{Draft ideas}
\subsection{Abstract}
\begin{itemize}
    \item What is the CLT? Why is formal verification important?
    \item What limitations or gaps does this work address?
    \item Briefly summarize the methods, results, and significance.
\end{itemize}
\section{Introduction}
\textbf{Purpose:} Set the stage for this thesis, establish its relevance, and provide an overview of the challenges and contributions.

\subsection{Background of the Central Limit Theorem (CLT)}
\begin{itemize}
    \item Briefly describe the CLT's significance in probability theory and its foundational role in various fields.
    \item Highlight the diversity of proofs for the CLT, focusing on Lyapunov’s direction as a generalization of the i.i.d. case.
\end{itemize}

\subsection{Formal Verification of Mathematical Theorems}   
\begin{itemize}
    \item Discuss the importance of formalizing theorems like the CLT for computational mathematics.
    \item Introduce HOL4 and its potential for advancing probability theory through rigorous formalization.
\end{itemize}

\subsection{Challenges and Motivation}
\begin{itemize}
    \item Outline the unique challenges of formalizing Lyapunov’s approach in HOL4:
    \item HOL4 lacks a robust library for complex analysis and probability.
    \item The proof depends on Taylor expansions, Big-O notation, and Lyapunov’s inequality, which needed to be formalized from scratch.
    \item Describe the failed attempt to use moment generating functions (MGFs) and how it inspired the shift to Lyapunov’s approach.
\end{itemize}

\subsection{Thesis Contributions}
\begin{itemize}
    \item Summarize key contributions:
    \begin{enumerate}
        \item Formalization of Lyapunov’s inequality in HOL4.
        \item Development of supporting libraries for Taylor expansions, Big-O notation, and moment analysis.
        \item Complete formalization of the CLT based on Lyapunov’s theorem.
    \end{enumerate}
\end{itemize}

\section{Background and Related Work}
\textbf{Purpose:} Position this work in the context of previous efforts and provide foundational concepts.
\subsection{Overview of the Central Limit Theorem}
\begin{itemize}
    \item Explain the statement of the CLT and its generalizations (e.g., Lyapunov’s and Lindeberg’s approaches).
    \item Focus on Lyapunov’s version as the basis of this proof:

     \begin{equation}
     \text{If } \frac{\Gamma_n}{s_n^3} \to 0 \text{ as } \space \space n \to \infty, 
     \end{equation}
     then 
     \[
     \frac{S_n}{s_n} \xrightarrow{d} \Phi. 
     \] 
     Define key terms: \( \Gamma_n, s_n, S_n \), and Lyapunov’s condition.
\end{itemize}

\subsection{Formal Proof Assistants in Probability Theory}
\begin{itemize}
    \item Discuss Isabelle/HOL and its use of characteristic functions to prove the CLT (mention Luke Serafin’s work briefly here).
    \item Highlight HOL4’s potential and this thesis's motivation to enrich its probability theory libraries.
\end{itemize}

\subsection{Lyapunov’s Direction and Proof Techniques}   
\begin{itemize}
    \item Provide an informal overview of Lyapunov’s proof steps:
    \begin{itemize}
        \item Construction of normal approximations (\( Y_j \)).
        \item Use of Taylor expansions to bound differences.
        \item Application of Lyapunov’s inequality to ensure convergence.
    \end{itemize}

   \item Contrast Lyapunov’s approach with other CLT proofs, emphasizing why it’s more suitable for HOL4’s existing framework.
\end{itemize}

\section{The Formalization Process}
\textbf{Purpose: Detail the technical challenges and solutions in formalizing Lyapunov’s proof in HOL4.}
\subsection{Overview of Lyapunov’s Proof Structure}
\begin{itemize}
    \item Provide a roadmap of the proof components you formalized:
    \begin{enumerate}
        \item Taylor expansions and approximation of test functions.
        \item Telescoping sums and bounding higher-order moments.
        \item Lyapunov’s inequality and its application to ensure convergence.
    \end{enumerate}
\end{itemize}

\subsection{Formalizing the Supporting Theorems in HOL4}
\begin{itemize}
    \item Taylor Expansion
    \item Big-O Notation
    \item Lyapunov’s Inequality
\end{itemize}

\subsection{Technical Challenges and Innovations}
\begin{itemize}
    \item Share how HOL4’s lack of complex analysis tools required alternative approaches (e.g., using Lyapunov’s proof instead of characteristic functions).
    \item ...
\end{itemize}

\section{The Formal Proof of the CLT in HOL4}
\textbf{Purpose:} Present the completed proof and validate its correctness.
\subsection{Step-by-Step Proof}
\begin{itemize}
    \item Present the formalized proof of Lyapunov’s theorem in HOL4.
    \item Break it into logical steps, mirroring the informal proof:
    \begin{enumerate}
        \item Setup and normalization of \( S_n \).
        \item Construction of \( Z_j \) and comparison with \( X_j \).
        \item Application of Taylor expansions and bounding error terms.
        \item Application of Lyapunov’s inequality to complete the proof.
    \end{enumerate}
\end{itemize}

\subsection{Validation and Soundness}  
\begin{itemize}
    \item Discuss how HOL4 ensures the proof’s correctness and soundness.
    \item Highlight key intermediate results that confirm the integrity of this thesis's approach.
\end{itemize}

\section{Results and Comparisons}
\textbf{Purpose:} Showcase the impact of this work and compare it to related efforts.
\subsection{Achievements in HOL4}
\begin{itemize}
    \item Summarize the completed formalization of Lyapunov’s CLT proof.
    \item  Highlight the additional libraries (e.g., Taylor expansions, Big-O notation) and their potential for future work.
\end{itemize}

\subsection{Comparison with Isabelle/HOL}
\begin{itemize}
    \item Briefly compare this work with Luke Serafin’s formalization of the CLT in Isabelle:
    \begin{itemize}
        \item HOL4 uses Lyapunov’s approach instead of characteristic functions.
        \item Discuss the trade-offs: HOL4’s modularity and flexibility versus Isabelle’s existing tools for complex analysis.
    \end{itemize}
\end{itemize}

\section{Conclusion}
\textbf{Purpose:} Reflect on the thesis’s contributions and look ahead.
\subsection{Summary of Contributions}
Restate achievements:
\begin{enumerate}
     \item Formalized Lyapunov’s theorem and the CLT in HOL4.
     \item  Extended HOL4’s libraries for probability theory.
     \item  Overcame challenges related to HOL4’s lack of complex analysis tools.
\end{enumerate}

Also, discuss the significance of enriching HOL4 for future formalizations in probability and functional analysis.

\subsection{Future Work}
Suggest potential extensions, such as:
\begin{itemize}
    \item Formalizing multivariate versions of the CLT.
    \item Extending HOL4’s libraries for advanced probabilistic theorems.
\end{itemize}

\subsection{Appendices and Supplementary Material}
Code listings, etc.

\subsection{The proof of Central Limit Theorem}
\subsubsection{Informal Proof}
Informal proof of Lyapounov's theorem for a single sequence by the method of Lindeberg \cite{chung2000course}.
\begin{itemize}
    \item \textbf{Notation and Statement}
    \begin{enumerate}
    \item \( \{X_j\}_{j=1}^n \) be a sequence of independent random variables with:
    \begin{itemize}
        \item[] \( \mathbb{E}[X_j] = 0 \), 
        \item[] \( \text{Var}(X_j) = \sigma_j^2 \) (finite variances, \( \sigma_j^2 < \infty \)),
        \item[] \( \mathbb{E}[|X_j|^3] = \gamma_j \) (finite third moments, \( \gamma_j < \infty \)).
    \end{itemize}

@@

### 2024-12-10 introduction.tex
Added Draft Outline of Thesis and Introduction

\chapter{Conclusion}
\label{concl}

asdfsdfasdf
\newpage
asdasasfdfdf

% \begin{figure*}
% \centering
% \includegraphics[width=0.98\textwidth]{Chapter1/Images/Fig1.pdf}
% \caption{caption}
% \label{figCh1:figure}
% \end{figure*}

\renewcommand\thefigure{\thechapter .\arabic{figure}}

>>>>

\chapter[Introduction]{Introduction}
\label{chap:1}

% \section{Introduction}
% \textbf{Purpose:} Set the stage for this thesis, establish its relevance, and provide an overview of the challenges and contributions.

% \subsection{Background of the Central Limit Theorem (CLT)}
% \begin{itemize}
%     \item Briefly describe the CLT's significance in probability theory and its foundational role in various fields.
%     \item Highlight the diversity of proofs for the CLT, focusing on Lyapunov’s direction as a generalization of the i.i.d. case.
% \end{itemize}

% \subsection{Formal Verification of Mathematical Theorems}   
% \begin{itemize}
%     \item Discuss the importance of formalizing theorems like the CLT for computational mathematics.
%     \item Introduce HOL4 and its potential for advancing probability theory through rigorous formalization.
% \end{itemize}

% \subsection{Challenges and Motivation}
% \begin{itemize}
%     \item Outline the unique challenges of formalizing Lyapunov’s approach in HOL4:
%     \item HOL4 lacks a robust library for complex analysis and probability.
%     \item The proof depends on Taylor expansions, Big-O notation, and Lyapunov’s inequality, which needed to be formalized from scratch.
%     \item Describe the failed attempt to use moment generating functions (MGFs) and how it inspired the shift to Lyapunov’s approach.
% \end{itemize}

% \subsection{Thesis Contributions}
% \begin{itemize}
%     \item Summarize key contributions:
%     \begin{enumerate}
%         \item Formalization of Lyapunov’s inequality in HOL4.
%         \item Development of supporting libraries for Taylor expansions, Big-O notation, and moment analysis.
%         \item Complete formalization of the CLT based on Lyapunov’s theorem.
%     \end{enumerate}
% \end{itemize}

Formal verification has continued revolutionizing the understanding and application of foundational theorems in mathematics: the surety of accompanying rigor and its implementation in computational systems. Thus have built chances for innovative mathematical services. Probability theory is a domain with both important theoretical results and practical applications, and it has increasingly become a focus of formalization efforts. The most important from such results is the Central Limit Theorem (CLT), which carries very strong implications in theory and practice.

The CLT is perhaps the most prominent result in probability theory describing how the sum of independent random variables, if suitably normalized, approximates a standard normal distribution when the number of terms increases indefinitely. It closes the gap between random single events and predictable behavior in the aggregate, forms the basis of inferential statistics, and underpins models in a vast variety of fields such as physics, finance, and artificial intelligence. Given this importance, formal verification of the CLT using proof assistants will be an important step toward proving its correctness in automated reasoning systems.

However, formalizing CLT is far from straightforward. There exist numerous variants of this theorem, together with their numerous proofs, ranging from classical independent and identically distributed (i.i.d.) to some more general versions, such as Lyapunov's theorem \cite{billingsley2017probability}. Each of those proofs uses advanced mathematical tools, including characteristic functions, moment generating functions, or even higher-order moments, according to the situation. These proofs require advanced mathematical infrastructure, which is not available with all proof assistants. In particular, the case of HOL4 \cite{slind2008brief} has found it impossible to use some of the approaches, particularly the one based on characteristic functions, because the strong complex analysis library was lacking.

Instead, this thesis follows another path: formalizing in the HOL4 proof assistant a generalized version of the CLT by Lyapunov's theorem. Lyapunov's approach is particularly appealing, as it has no direct use of either complex analysis or characteristic functions. Instead, it pays attention to moment-based convergence criteria, trying to provide its conditions for convergence using Taylor expansions, Big-O notation of error bounds, and Lyapunov's inequality. This approach aligns well with the existing mathematical infrastructure of HOL4 while simultaneously expanding its capabilities.

This project formalizes Lyapunov's proof in HOL4 and demonstrates the feasibility of verifying advanced probabilistic results in HOL4. More specifically, it has added:
\begin{itemize}
    \item Formally defined Taylor expansions in function bounds and error terms.
    \item Big-O, allowing accurate representations of asymptotic behavior.
    \item Lyapunov's inequality, the key condition for the convergence between the CLT.
\end{itemize}

\section{Motivation}
The formalization of the Central Limit Theorem in HOL4 involved interesting challenges because of the highly mathematical nature of the theorem and the specific limitations of existing libraries in HOL4. Another difference between the proof assistants, Isabelle/HOL, which has a very mature library for complex analysis and HOL4, is that there are no built-in key concepts for working with characteristic functions and others associated with the common classical proofs of CLT.

Lack of a well-developed library has been one of the major setbacks of HOL4. Proving the central limit theorem using the more traditional kinds of proofs, such as the one formalized in Isabelle/HOL, involves the use of characteristic functions for convergence proof. Characteristic functions are essentially Fourier transforms and thereby hinge a lot on complex analysis. It would have been very difficult to follow this approach in HOL4, since the proof assistant currently lacks support for these advanced tools.

An alternative approach was explored using moment generating functions (MGFs). MGFs are much more popular for proving the CLT, wherein their specialized property is utilized to show convergence to the standard normal distribution. However, it soon became evident that formally establishing the uniqueness property of MGFs would become a serious blocker. While this property is a triviality in classical analysis, the formalization work involved was highly intricate and beyond the scope of what is currently practical within HOL4's libraries. As a result, this approach was abandoned, leading to the need for a new direction.

The breakthrough came with the adoption of Lyapunov's theorem as the basis for formalizing the CLT.  Lyapunov's argument has a very direct and elementary approach to the theorem without using complex analysis or moment-generating functions but rather basing on real-valued, moment-based convergence criteria; hence, it being particularly fitted into the existing framework of HOL4. Lyapunov's proof is a milestone of abstraction in the probability theory, but it is still beautifully simple and thus met the practical and strict requirements of formal verification.

However, Lyapunov’s method introduced its own set of challenges for formalization in HOL4:
\begin{itemize}
    \item \textbf{Taylor Expansions:} The proof relies heavy on Taylor expansions to approximate test functions and bound errors. These had to be rigorously formalized in HOL4 from first principles.
    \item \textbf{Big-O Notation:} Reasoning about the asymptotic behavior of error terms involved the formalization of Big-O notation, which did not exist in HOL4 until now.
    \item \textbf{Lyapunov's Inequality:} An important part of the proof was the formalization of Lyapunov's inequality, which gives sufficient conditions for convergence. It was carefully adapted to fit into HOL4's logical framework.
\end{itemize}

Following the Lyapunov's approach, with its valuation on real techniques and elementary methods, proved most important: it served to encapsulate the CLT under the constraints of HOL4 and was entirely consistent toward building reusable mathematics libraries. Taylor series developments, Big-O notion, and Lyapunov's inequality are indispensable not only for this proof but also as a basis of further formalizations in the realm of probability theory and elsewhere.

This shift from characteristic functions and MGFs to the more concrete, moment-based approach of Lyapunov underlines flexibility and problem-solving ingenuity necessary in formal verification projects. It thus shows how advanced mathematical results can be formalized in HOL4, even when serious deficiencies in its infrastructure must first be overcome. Moreover, it emphasizes the role of Lyapunov's approach as a turning point in the history of probability theory and as one of the bases for modern formalization.

\section{Structure of the Thesis}
The rest of the thesis is organized as follows. Chapter 2 provides background on the Central Limit Theorem, its history, and the setting of Lyapunov's proof. Related work, including other formalizations, using proof assistants like Isabelle/HOL is also covered. Chapter 3 then details the formalization, discussing the challenges faced along with solutions developed, in particular the formalization of Taylor expansions, Big-O notation and Lyapunov's inequality. The key components of the proof, its completion, and its validation of the CLT are discussed in Chapter 4. Chapter 5 presents a discussion of results, and positioning of this work with respect to related efforts on formal verification. Finally, the thesis is concluded in Chapter 6 by summarizing the contributions made by this work and presenting the vision on future directions that probability theory in HOL4 may take.

This thesis not only shows that a formalization of the CLT in HOL4 is possible but also opens up further opportunities for work on the formal probability theory. It fills in some foundational gaps and provides reusable tools, which illustrates more general potential of HOL4 to make serious contributions to the fully verified mathematics corpus.
